A Bayesian networks approach to infer social changes from burials in northeastern Taiwan during the European colonization period

### 2021-08-24 analysis/paper/paper.Rmd
knitting succeeded!

```{r read-models-data, include=FALSE}
load(here::here("analysis", "data", "derived_data", "burial_bergm_model.RData"))
readRDS(here::here("analysis", "data", "derived_data", "pre_bergm.rds"))
readRDS(here::here("analysis", "data", "derived_data", "post_bergm.rds"))
```

>>>>

```{r read-models-data, include=FALSE}
load(here::here("analysis", "data", "derived_data", "burial_bergm_model.RData"))
```
